Stock enhancement undermines community stability

### 2022-01-30 rmd/supporting_info.Rmd
Update supporting_info.Rmd

```{=tex}
\begin{align}
\phi_i = 
\left\{
\begin{array}{cc}
f_R & (i = 1)\\
0 & (i \ne 1)
\end{array}
\right.
\end{align}
```
$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. The equation (2) can be reorganized to:

```{=tex}
\begin{align}
N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
\end{align}
```
In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively. We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of release $(R_t=R)$.

@@

Under each parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates). The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$. We initialized the community with populations of each species drawn from a Poisson distribution with a mean of five. We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach an equilibrium without stock enhancement (initialization period). After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach a new equilibrium with selective stock enhancement (burn-in period). We continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps. We obtained the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the number of species persist (defied as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the SD ($\sigma$). The temporal mean and SD were also calculated for the enhanced species ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately. We summarized values of simulation parameters in **Table S1**.

@@

**Time-series data.** We assembled time-series data of fish abundance across `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan. At these sites, the long-term monitoring program began in 1971 but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented since 1999. Most data were collected in summer with irregular interannual intervals (1- to 3-year interval for most cases). We confined our analysis to the sites that meets the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon are observed at least twice during the observation period. As a result, we used time-series data of fish abundance at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds during a period of 1999-2019. **Table S5** summarizes observed species in these watersheds.

**Fish stocking.** At the protected watersheds, stocking of masu salmon began in 1950s. Hatchery fish were released in spring (fry [age 0+] and smolt [age 1+] stages) and fall (juvenile stage [age 0+]). For each watershed, we examined historical records and assembled annual data of stock enhancement (the number of fish released) for a period of 1999-2019. Although fish were released at multiple locations within a watershed, we were unable to extract stocking data at the site level.

**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]). We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site. The proportion of forest land use in each watershed polygon was estimated based on land-use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020]. Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018]. Annual data of ocean productivity (2003-2019) were extracted from OceanColor ([\<https://oceancolor.gsfc.nasa.gov/\>](https://oceancolor.gsfc.nasa.gov/){.uri}) and the average value within the 30-km radius of each river mouth was calculated. We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*

@@

Our goal is to compare temporal community dynamics across sites. However, the data are not directly comparable because of observation errors (e.g., different observers) and missing observations. To confront this challenge, we developed a Bayesian state space model for three species groups separately: (i) whole community, summed abundance of all species, (ii) enhanced species, abundance of masu salmon, (iii) unenhanced species, summed abundance of all species except masu salmon. A Bayesian state space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004; @keryBayesianPopulationAnalysis2012]. The model is composed of observation and state models as described below.

@@

```{=tex}
\begin{align}
\lambda_{s,t} = n_{s,t}exp(\epsilon_{s,t}^{obs}) + \psi \beta_s~Fry_{w(s),t}
\end{align}
```
$n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density. The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$. The parameter $\epsilon_{s,t}^{obs}$ is the normally-distributed error term ($\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$) that accounts for site- and year-specific observation errors. When modeling the unenhanced species group, $\psi$ equals zero (otherwise $\psi = 1$) so the model excludes the term $\beta_s~Fry_{w(s),t}$.

@@

```{=tex}
\begin{align}
ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state}
\end{align}
```
where $ln~r_{s}$ is the site-specific rate of change at site $s$, and $\epsilon_{s,t}^{state}$ is the process error that follows a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$. The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$). This hierarchical structure allows for improved estimates of $ln~r_s$ by sharing information across sites. We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$). Bayesian p-values [@keryIntroductionWinBUGSEcologists2010] for the state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate. Estimated parameters and community dynamics are summarized in Supporting Information (**Table S7** and **Figures S13-S15**).

We developed the following linear regression model taking either CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or Poisson distribution.

```{=tex}
\begin{align}
\left\{
\begin{aligned}
ln~y_s &\sim Normal(\mu_y, \sigma_y^2) &&\text{for CV, mean, and SD}\\
y_s &\sim Poisson(\mu_{y,s}exp(\epsilon_{y,s})) &&\text{for species richness}
\end{aligned}
\right.
\end{align}
```
where $\sigma_y$ is the SD of residual errors and $\epsilon_{y,s}$ is the normally-distributed error term that accounts for overdispersion ($\epsilon_{y,s} \sim Normal(0, \sigma_y^2)$). The expected mean $\mu_y$ was related to linear predictors as follows:

```{=tex}
\begin{align}
\left\{
\begin{aligned}
\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD}\\
ln~\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
\end{aligned}
\right.
\end{align}
```
$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictor $x_k$. The site-level predictors include upstream watershed area, air temperature, precipitation, and forest land use (fraction). The watershed-specific intercept was related to watershed-level predictors as:

```{=tex}
\begin{align}
\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
\end{align}
```
$\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients. The watershed-level predictors $z_{k,w}$ include the number of masu salmon released (average of 1999-2019) and ocean productivity (Chlorophyll a). The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that cannot be captured by the watershed-level predictors.

We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016]. We assigned weakly informative priors for parameters, which were summarized in **Table S6**. Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].

@@

We performed a sensitivity analysis of the community simulation to identify key simulation parameters that strongly affect the relationships between community dynamics (temporal mean and SD of density) and stock enhancement. We generated 500 sets of parameter combinations by randomly drawing values of 7 simulation parameters from uniform distributions (**Table S1**). For each parameter combination, we simulated dynamics of 100 independent communities with varying numbers of stock enhancement $R$ (drawn randomly from $Unif(0, 500)$). This yields a total of 50000 simulation replicates. In each simulation replicate, we ran 1600 time steps of community dynamics and obtained temporal means and SDs of whole community ($\sum_i^SN_i$), enhanced species ($N_1$), and unenhanced species ($\sum_{i, i\ne1}^SN_i$) using the last 1000 time steps. The first 600 time steps were discarded as initialization and burn-in periods.

For each parameter combination, we regressed mean densities and SDs of whole community, enhanced species, and unenhanced species $y_j$ on the number of release $R$ as:

@@

where $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$). Both response and explanatory variables were standardized to a mean of zero and a standard deviation of one, so that regression coefficients are comparable.

@@

Parameter values used in the main and sensitivity analysis. In the sensitivity analysis, 500 parameter values were drawn randomly from uniform distributions. See Methods for model description.

@@

  table_legend <- paste0("Sensitivity analysis of the community simulation. Parameter estimates of linear regression models (standard errors in parenthesis) are shown. Response variables are the effects of stock enhancement on temporal mean density ($\\mu$) and SD ($\\sigma$) of ", c_text[i],". Both response and explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one prior to the analysis.")

@@

## Table S7 Parameter estimates of the Bayesian state space model

Median estimates of the Bayesian state space model. Site specific parameters were excluded due to the large number of parameters. Numbers in parenthesis indicate 95% credible intervals.

@@

                       "Theoretical predictions for the stocking effect on community dynamics. Rows represent different response varaibles, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$). Other parameters are: ",
                       "intrinsic growth rate of enhanced species $r_1$ = `r df_param$r1[",i,"]`; ",
                        "environmental variability $\\sigma_{\\epsilon}$ = `r df_param$sd_env[",i,"]`; ",
                        "carrying capacity $K$ = `r df_param$k[",i,"]`.",
                        "\n\\pagebreak\n")

@@

                       "\n```{r figure_s", i + j,", fig.width = 11, fig.height = 8}
                       \n\n
                       list_g_dyns[[",i,"]]
                       \n\n
                       ```\n",
                       "Temporal dynamics of stream fish communities (`r c_text[",i,"]`) in Hokkaido, Japan. Dots represent observed density, and solid lines are predicted values of the Bayesian state-space model. Panels correspond to individual watersheds, and colors distinguish samplig sites within a watershed.",
                        "\n\\pagebreak\n")

>>>>

```{=tex}
\begin{align}
\phi_i = 
\left\{
\begin{array}{cc}
f_R & (i = 1)\\
0 & (i \ne 1)
\end{array}
\right.
\end{align}
```
$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Equation (2) can be reorganized to:

```{=tex}
\begin{align}
N_{i,t+1} = [N_{i,t}+\phi_i R_t]exp \left[r_i \left(1-\frac{N_{i,t}+\alpha_{i1}R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
\end{align}
```
In this model, intrinsic growth rates of unenhanced species $r_{i,i \ne 1}$ and interspecific competition $\alpha_{ij}$ are random draws from a uniform ($r_{i,i \ne 1} \sim Unif(0,r_{max})$) and an exponential distribution ($\alpha_{ij} \sim Exp(1/\bar{\alpha})$), respectively. We assumed constant values of intraspecific competition ($\alpha_{ii}=1$), carrying capacity $(K_i = K)$ and the number of releases $(R_t=R)$.

@@

Under each parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates). The number of released individuals $R$ was drawn randomly from a uniform distribution for each simulation replicate as $R \sim Unif(0,500)$. We initialized the community with populations of each species drawn from a Poisson distribution with a mean of five. We repeated the seeding procedure every 10 time steps over the first `r unique(sim_result$n_warmup)` time steps to allow species to establish populations and reach equilibrium without stock enhancement (initialization period). After the initialization period, we released $R$ individuals of the enhanced species every time step over the next `r unique(sim_result$n_burnin)` time steps to reach new equilibrium with selective stock enhancement (burn-in period). We continued the simulation run with stock enhancement and saved the last `r unique(sim_result$n_timestep)` time steps. We obtained the following summary statistics of the whole community $\sum_i^SN_j$: the coefficient of variation (CV), the number of species persist (defied as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the SD ($\sigma$). The temporal mean and SD were also calculated for the enhanced species ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately. We summarized values of simulation parameters in **Table S1**.

@@

**Time-series data.** We assembled time-series fish data across `r n_distinct(d0$site_id)` sites within `r n_distinct(d0$river)` protected watersheds of Hokkaido Island, Japan. A long-term monitoring program began at these sites in 1971, but effective sampling methods (a combination of electrofishing and cast net sampling) were implemented in 1999. Most data were collected in summer with irregular interannual intervals (1- to 3-year intervals for most cases). We confined our analysis to the sites that meet the following criteria: (i) the observation span (from the first to the last year of observation) exceeds 10 years, (ii) the number of observation years exceeds five years, and (iii) masu salmon is observed at least twice during the observation period. As a result, we used time-series data at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` watersheds from 1999 to 2019. **Table S5** summarizes observed species in these watersheds.

**Fish stocking.** At the protected watersheds, the stocking of masu salmon began in the 1950s. Hatchery fish were released in spring (fry [age 0+] and smolt [age 1+] stages) and fall (juvenile stage [age 0+]). For each watershed, we examined historical records and assembled annual data of stock enhancement (the number of fish released) from 1999 to 2019. Although fish were released at multiple locations within a watershed, we could not extract stocking data at the site level.

**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest), local climates (annual mean air temperature [degree Celsius] and cumulative precipitation [mm]), and ocean productivity (Chlorophyll a [unit]). We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site. We estimated the proportion of forest land use in each watershed polygon based on land-use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020]. Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018]. Annual data of ocean productivity (2003-2019) were extracted from OceanColor ([\<https://oceancolor.gsfc.nasa.gov/\>](https://oceancolor.gsfc.nasa.gov/){.uri}) and we calculated the average value within the 30-km radius of each river mouth. We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*

@@

Our goal is to compare temporal community dynamics across sites. However, the data are not comparable because of observation errors (e.g., different observers) and missing observations. To confront this challenge, we developed a Bayesian state-space model for three species groups separately: (i) whole community, summed abundance of all species, (ii) enhanced species, the abundance of masu salmon, (iii) unenhanced species, summed abundance of all species except masu salmon. A Bayesian state-space model is best suited for our analysis because it can account for observation errors while imputing missing values given the long-term trend at each site [@clarkPopulationTimeSeries2004; @keryBayesianPopulationAnalysis2012]. The model is composed of observation and state models, as described below.

@@

```{=tex}
\begin{align}
\lambda_{s,t} = n_{s,t}exp(\epsilon_{s,t}^{obs}) + \psi \beta_s~Fry_{w(s),t}
\end{align}
```
$n_{s,t}$ is the "true" fish density excluding fish released in the spring, $Fry_{w(s),t}$ the number of salmon fry released in spring in watershed $w$ within which site $s$ is located, and $\beta_s$ the site-specific effect of released salmon fry on the observed fish density. The parameter $\beta_s$ was drawn from a normal distribution with the hyper-mean $\mu_{\beta}$ and hyper-variance $\sigma_{\beta}^2$. The parameter $exp(\epsilon_{s,t}^{obs})$ is the error term that follows a log-normal distribution ($\epsilon_{s,t}^{obs} \sim Normal(0, \sigma_{obs,s}^2)$). The inclusion of this term allows the model to account for site- and year-specific observation errors, which can be caused by ecological and/or artificial factors. When modeling the unenhanced species group, $\psi$ equals zero (otherwise $\psi = 1$) so the model excludes the term $\beta_s~Fry_{w(s),t}$.

@@

```{=tex}
\begin{align}
ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state}
\end{align}
```
where $ln~r_{s}$ is the site-specific rate of change at site $s$, and $\epsilon_{s,t}^{state}$ is the process error that follows a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$. The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the standard deviation $\sigma_r$). This hierarchical structure allows for improved estimates of $ln~r_s$ by partially sharing information across sites [@gelmanDataAnalysisUsing2007]. We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$).

We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0-1 and indicates over- (\~0.0), under- (\~1.0), or suitable-fitting (\~0.5) to the data. Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate. **Table S7** and **Figures S13-S15** summarize estimated parameters and community dynamics.

We developed the following linear regression model taking either CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.

```{=tex}
\begin{align}
\left\{
\begin{aligned}
ln~y_s &\sim Normal(\mu_{y,s}, \sigma_y^2) &&\text{for CV, mean, and SD}\\
y_s &\sim Poisson(\mu_{y,s}exp(\epsilon_{y,s})) &&\text{for species richness}
\end{aligned}
\right.
\end{align}
```
where $\sigma_y$ is the SD of residual errors and $exp(\epsilon_{y,s})$ is the error term that accounts for overdispersion ($\epsilon_{y,s} \sim Normal(0, \sigma_y^2)$). The expected mean $\mu_y$ was related to linear predictors as follows:

```{=tex}
\begin{align}
\left\{
\begin{aligned}
\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD}\\
ln~\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
\end{aligned}
\right.
\end{align}
```
$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictors $x_k$. The site-level predictors include upstream watershed area, air temperature, precipitation, and proportion of forest land use. The watershed-specific intercept was related to watershed-level predictors as:

```{=tex}
\begin{align}
\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
\end{align}
```
$\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients. The watershed-level predictors $z_{k,w}$ include the number of masu salmon released (average of 1999-2019) and ocean productivity (Chlorophyll a). The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture. All predictors were standardized (mean = 0, SD = 1) before the analysis.

We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016]. We assigned weakly informative priors to parameters (**Table S6**). Data manipulation and analysis were performed in R version 4.1.0 [@rcoreteamLanguageEnvironmentStatistical2021].

@@

We performed a sensitivity analysis of the community simulation to identify key simulation parameters that strongly affect the relationships between community dynamics (temporal mean and SD of density) and stock enhancement. We generated 500 sets of parameter combinations by randomly drawing values of 7 simulation parameters from uniform distributions (**Table S1**). For each parameter combination, we simulated dynamics of 100 independent communities with varying numbers of stock enhancement $R$ (drawn randomly from $Unif(0, 500)$). This yields a total of 50000 simulation replicates. In each simulation replicate, we ran 1600 time steps of community dynamics and obtained temporal means and SDs of the whole community ($\sum_i^SN_i$), enhanced species ($N_1$), and unenhanced species ($\sum_{i, i\ne1}^SN_i$) using the last 1000 time steps. The first 600 time steps were discarded as initialization and burn-in periods.

For each parameter combination, we regressed mean densities and SDs of the whole community, enhanced species, and unenhanced species $y_j$ on the number of releases $R$ as:

@@

where $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$). Both response and explanatory variables were standardized to a mean of zero and a standard deviation of one to compare regression coefficients.

@@

Parameter values used in the main and sensitivity analysis. Five hundred parameter values were drawn randomly from uniform distributions in the sensitivity analysis.

@@

  table_legend <- paste0("Sensitivity analysis of the community simulation. Parameter estimates of linear regression models (standard errors in parenthesis) are shown. Response variables are the effects of stock enhancement on temporal mean density ($\\mu$) and SD ($\\sigma$) of ", c_text[i],". Both response and explanatory variables (i.e., simulation parameters) were standardized to a mean of zero and a standard deviation of one before the analysis.")

@@

## Table S7 Parameter estimates of the Bayesian state-space model

Median estimates of the Bayesian state-space model. Numbers in parenthesis indicate 95% credible intervals. Site-specific parameters were excluded due to a large number of parameters.

@@

                       "Theoretical predictions for the stocking effect on community dynamics. Rows represent different response variables, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$). Other parameters are: ",
                       "intrinsic growth rate of enhanced species $r_1$ = `r df_param$r1[",i,"]`; ",
                        "environmental variability $\\sigma_{\\epsilon}$ = `r df_param$sd_env[",i,"]`; ",
                        "carrying capacity $K$ = `r df_param$k[",i,"]`.",
                        "\n\\pagebreak\n")

@@

                       "\n```{r figure_s", i + j,", fig.width = 11, fig.height = 8}
                       \n\n
                       list_g_dyns[[",i,"]]
                       \n\n
                       ```\n",
                       "Temporal dynamics of stream fish communities (`r c_text[",i,"]`) in Hokkaido, Japan. Dots represent observed density, and solid lines are the predicted values of the Bayesian state-space model. Panels correspond to individual watersheds, and colors distinguish sampling sites within a watershed.",
                        "\n\\pagebreak\n")
